The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-10-13 manuscript.Rmd
refine record deduplication

>>>>

To generate the combined list of records from iDigBio and OBIS, we removed putative duplicate based on the following criteria: same phylum, same accepted species name from WoRMS, same geographic coordinates (rounded to the 4th decimal), and same date of collection. When the date is missing, a single record per species with identical coordinates is included.
